State of the Practice for Medical Imaging Software Based on Open Source Repositories

### 2024-06-05 StateOfPractice/Papers/SOP_MI_OSR/SOP_MI_OSR.tex
Add roadmap for subsections of Section 3 (Discussion)

The review section shows us how the ranking between the existing open source MI
software, but does our ranking match how practitioners in the field rank the
software.  how does our ranking compare to the software compare to other
compares compare to community ranking and look at artifacts.

>>>>

In Section~\ref{Sec_VsCommunityRanking}, we compare our ranking to the MI
software community's ranking, as a way to judge our results, and a way to
understand what the MI community currently values. To understand the state of
the practice for MI software relative to other software, we compare MI software
to other research software in Section~\ref{Sec_CompareArtifacts}.  The
comparison is based on the artifacts our measurement exercise found in the MI
repositories, versus what is typically recommended for research software.  We
also discuss potential reasons to doubt our results in the threats to validity
section (Section~\ref{sec_threats_to_validity}).
